\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
% Make lists more compact
% \setlist[itemize]{itemsep=0.25ex, topsep=0.25ex, parsep=0ex, partopsep=0ex}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{setspace}
% Silence underfull hbox warnings and improve line breaking
\hbadness=10000
\emergencystretch=3em

% Page margins
\geometry{a4paper, margin=1in}

% Hyperlink setup
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
    pdftitle={Resume - Do Van Duy},
    pdfpagemode=FullScreen,
}

% Section title format
\titleformat{\section}{\Large\bfseries\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3ex}{2ex}

% Subsection title format
\titleformat{\subsection}{\large\bfseries}{}{0em}{}
\titlespacing{\subsection}{0pt}{1ex}{1ex}

% Document begins
\begin{document}

% Header with left-aligned name and right-aligned contact info
\noindent
\begin{minipage}[t]{0.60\textwidth}
    \Huge\scshape Do Van Duy
\end{minipage}%
\begin{minipage}[t]{0.40\textwidth}
    \raggedleft
    \normalsize
    \href{mailto:hello@duyne.me}{Email: hello@duyne.me}\\
    \href{tel:+84971210898}{Phone: +84 971210898}\\
    \href{https://duyne.me}{Blog: duyne.me}\\
    \href{https://github.com/duyhenryerz}{GitHub: duyhenryer}\\
    \href{https://linkedin.com/in/duyne}{LinkedIn: Duy nè}
\end{minipage}
\vspace{0.75em}


% Overview
\section{Overview}
\begingroup
\setstretch{1.2}
Over 5 years of dedicated DevOps experience, including proficiency in cloud environments like AWS \& GCP. A forward-thinking DevOps Engineer with a robust background in optimizing operating systems within agile frameworks. Specializing in the strategic deployment of technologies like Terraform, AWS, Kubernetes, and GitOps principles, I ensure scalable, efficient, and innovative IT infrastructures. My expertise extends to automating workflows, crafting CI/CD pipelines, and integrating GitOps for enhanced operational clarity and consistency.
\endgroup

% Skills Summary
\section{Skills Summary}
\begin{itemize}[leftmargin=*, label={}]
    \item \textbf{Languages:} Python, Bash
    \item \textbf{Infrastructure \& Platform:} Kubernetes, Docker and GitOps(fluxcd)
    \item \textbf{Monitoring \& Logging:} VictoriaMetrics, Prometheus, Grafana, Loki, Graylog
    \item \textbf{CI/CD:} GitHub Actions, Jenkins, GitLab CI
    \item \textbf{Storage Engines:} Elasticsearch, Kafka, RabbitMQ, Redis, PostgreSQL, ScyllaDB, MySQL, MongoDB
    \item \textbf{Cloud \& Tools:} AWS, GCP, Terraform, Git, Cloudflare, Temporal, Vault, KEDA,
    \item \textbf{Networking:} TCP/IP, DNS, SSH, SSM, telnet.
    \item \textbf{Soft Skills:} Responsibility, Problem Solving, Communication, Teamwork, Time Management    
\end{itemize}

% Work Experience
\section{Work Experience}
\textbf{\href{https://www.opswat.com/}{Opswat}} \hfill {\small\textit{Onsite / Ho Chi Minh, Vietnam}} \\
\textit{Site Reliability Engineer II} \hfill {\small\textit{December 2024 - Now}}
\begin{itemize}[leftmargin=*]
    \item Migrated and standardized Terraform infrastructure across environment IaC tools like Terraform.
    \item Unified multi-environment GitOps workflows on EKS using FluxCD and Kustomize.
    \item Built observability and enhanced the stack with Prometheus, Grafana, and VictoriaMetrics, and reduced downtime by 20%
    \item Implemented logging with Loki and VictoriaLogs solutions that enhanced system observability and troubleshooting.
    \item Developed and maintained Helm charts for internal cloud deployments and customer release packaging.
    \item Managed CI/CD pipelines using TeamCity for automated build and deployment.
    \item Built RPM packages of cloud applications for customer on-premise.
    \item Operated core data services including NGINX Ingress, MongoDB, Redis, RabbitMQ.
    \item Networking experience with TCP/IP, DNS, SSH, telnet, SSM, etc.
    \item Tracked and managed tasks with Jira/Confluence.
\end{itemize}

\vspace{0.5em}
\textbf{\href{https://www.chotot.com/}{ChoTot}} \hfill {\small\textit{Onsite / Ho Chi Minh, Vietnam}} \\
\textit{DevOps Engineer} \hfill {\small\textit{July 2022 - December 2024}}
\begin{itemize}[leftmargin=*]
    \item Migrated On-Premise staging to GCP with optimized databases and storage for cost efficiency.
    \item Modernized Kubernetes clusters and leveraged GKE Spot workloads to achieve a 30\% reduction in compute costs without service disruption.
    \item Managed CI/CD pipelines with GitHub Actions, contributing reusable workflows.
    \item Managed server-side and ingress technologies including Nginx, Nginx Ingress, and Kong.
    \item Utilized Terraform for infrastructure as code on GCP and AWS.
    \item Hands-on with databases: MySQL, MongoDB, Redis, PostgreSQL, ScyllaDB.
    \item Developed and contributed to Helm charts for managing applications.
    \item Replaced Bastion hosts with Cloudflare Zero Trust, improving access control.
    \item Implemented monitoring and logging with Prometheus, Grafana, and VictoriaMetrics.
    \item Defined SLI/SLOs to optimize reliability and latency (HTTP/gRPC), improving response times by 25\% and ensuring 99.9\% uptime.
    \item Networking experience with TCP/IP, DNS, DHCP, SSH.
    \item Responded to incidents, troubleshot system issues, and provided night support to ensure smooth releases and operations.
    \item Tracked and managed tasks with Jira/Confluence.
\end{itemize}

\vspace{0.5em}
\textbf{\href{https://spores.app/}{Spores}} \hfill {\small\textit{Remote / Ho Chi Minh, Vietnam}} \\
\textit{DevOps Engineer} \hfill {\small\textit{October 2021 - July 2022}}
\begin{itemize}[leftmargin=*]
    \item Managed and deployed applications across Development, Testnet, and Mainnet environments.
    \item Built CI/CD pipelines with GitHub Actions, CodeCommit, and ArgoCD for GitOps.
    \item Used Terraform for AWS infrastructure and Graph\-Node for block\-chain data in\-dex\-ing (Ethereum, BSC, Polygon).
    \item Hands-on experience with databases such as MySQL, Redis, PostgreSQL, and AWS services.
    \item Deployed and maintained monitoring and logging tools such as Prometheus, Grafana, and Loki.
    \item Tracked and managed tasks with Jira/Confluence.
\end{itemize}

\vspace{0.5em}
\textbf{\href{https://firegroup.io/}{FireGroup}} \hfill {\small\textit{Onsite / Ho Chi Minh, Vietnam}} \\
\textit{System Engineer} \hfill {\small\textit{May 2020 - October 2021}}
\begin{itemize}[leftmargin=*]
    \item Migrated legacy systems to AWS, building new infrastructure from scratch.
    \item Designed CI/CD pipelines using Jenkins, GitHub Actions, and GitLab CI.
    \item Managed GitOps deployments with Helm and FluxCD on EKS.
    \item Utilized Terraform for infrastructure as code on AWS across staging, UAT, and production.
    \item Hands-on with databases: MySQL, MongoDB, Redis, PostgreSQL; and a broad set of AWS services.
    \item Operated server-side technologies such as Nginx; cloud-native ingress like Nginx Ingress and Kong Ingress.
    \item Implemented monitoring and logging using the EFK stack, Prometheus \& Grafana, and AWS CloudWatch.
    \item Tracked and managed tasks with Jira/Confluence.
\end{itemize}


% Education
\section{Education}
\textbf{Ton Duc Thang University} \hfill Ho Chi Minh, Vietnam \\
\textit{\textbf{Bachelor of Science in Computer Science}} \hfill August 2015 - October 2021 \\
\textit{Courses:} Data Structures, Networking, Operating System, Database, Multimedia Programming, Software Engineering

\end{document}
